Fair Queuing Aware Congestion Control

### 2022-06-23 tex/paper.tex
Typo in results

\begin{table}
\begin{tabularx}{\columnwidth}{| l | X | X | X |}
\hline
& 10 Mbit/s & 50 Mbit/s & 100 Mbit/s \\ \hline
10ms & Median: 100\% \newline 1st quart.: 99\% \newline 3rd quart.: 100\% & Median: 100\% \newline 1st quart.: 100\% \newline 3rd quart.: 100\% & Median: 100\% \newline 1st quart.: 98\% \newline 3rd quart.: 99\%\\ \hline
50ms & Median: 100\% \newline 1st quart.: 100\% \newline 3rd quart.: 100\% & Median: 100\% \newline 1st quart.: 100\% \newline 3rd quart.: 100\% & Median: 100\% \newline 1st quart.: 100\% \newline 3rd quart.: 100\% \\ \hline
100ms & Median: 100\% \newline 1st quart.: 98\% \newline 3rd quart.: 100\% & Median: 100\% \newline 1st quart.: 100\% \newline 3rd quart.: 100\% & Median: 100\% \newline 1st quart.: 100\% \newline 3rd quart.: 100\% \\ \hline
\end{tabularx}
\caption{Detection accuracy in case there's \textbf{no fair queuing} under the presence of \textbf{cross-traffic}. The overall median accuracy is 100\%, the first quartile is 100\% and the third quartile is 100\%.}
\label{table:no_fq_crosstraffic}
\end{table}

>>>>

\begin{table}
\begin{tabularx}{\columnwidth}{| l | X | X | X |}
\hline
& 10 Mbit/s & 50 Mbit/s & 100 Mbit/s \\ \hline
10ms & Median: 99\% \newline 1st quart.: 98\% \newline 3rd quart.: 99\% & Median: 100\% \newline 1st quart.: 100\% \newline 3rd quart.: 100\% & Median: 100\% \newline 1st quart.: 100\% \newline 3rd quart.: 100\%\\ \hline
50ms & Median: 100\% \newline 1st quart.: 100\% \newline 3rd quart.: 100\% & Median: 100\% \newline 1st quart.: 100\% \newline 3rd quart.: 100\% & Median: 100\% \newline 1st quart.: 100\% \newline 3rd quart.: 100\% \\ \hline
100ms & Median: 100\% \newline 1st quart.: 100\% \newline 3rd quart.: 100\% & Median: 100\% \newline 1st quart.: 100\% \newline 3rd quart.: 100\% & Median: 100\% \newline 1st quart.: 98\% \newline 3rd quart.: 100\% \\ \hline
\end{tabularx}
\caption{Detection accuracy in case there's \textbf{no fair queuing} under the presence of \textbf{cross-traffic}. The overall median accuracy is 100\%, the first quartile is 100\% and the third quartile is 100\%.}
\label{table:no_fq_crosstraffic}
\end{table}
